Unknown

### 2024-03-06 ms/ms.qmd
started adding latex shortcuts to ms

---
title: Unknown
format:
  pdf:
    keep-tex: true  
    toc: false
header-includes: |
  \addtokomafont{disposition}{\rmfamily}
  \usepackage{siunitx}
mainfont: Times New Roman
csl: https://www.zotero.org/styles/science
---

@@

### Amphistomy advantage

We estimated 'amphistomy advantage' ($\mathrm{AA}$) *sensu* @parkhurst_adaptive_1978, but with modifications previously described in @triplett_amphistomy_2024. $\mathrm{AA}$ is calculated as the log-response ratio of $A$ compared at the same total $g_\text{sw}$:

@@

We measured the photosynthetic rate of an untreated amphistomatous leaf ($A_{\mathrm{amphi}}$) over a range of $g_\text{sw}$ values. We refer to this as an $A \textendash g_\text{sw}$ curve. We compared the $A \textendash g_\text{sw}$ curve of the untreated leaf to the photosynthetic rate of pseudohypostomatous leaf ($A_\mathrm{hypo}$), which is the same leaf but with gas exchange through the upper surface blocked by a neutral density plastic (propafilm).

We measured $A \textendash g_\text{sw}$ curves using a portable infrared gas analyzer (LI-6800PF, LI-COR Biosciences, Lincoln, Nebraska, USA). Light-acclimated plants were placed under LEDs dimmed to match their light treatment during gas exchange measurements. We estimated the photosynthetic rate ($A$) and stomatal conductance to water vapor ($g_\text{sw}$) at ambient CO$_2$ (415 ppm) and $T_\mathrm{leaf} = \qty{25.0}{\degreeCelsius}$. The irradiance of the light source in the pseudohypo leaf was higher because the propafilm reduces transmission. To compensate for reduced transmission, we increased incident $\mathrm{PPFD}$ for pseudohypo leaves by a factor 1/0.91, the inverse of the measured transmissivity of the propafilm. We also set the stomatal conductance ratio, for purposes of calculating boundary layer conductance, to 0 for pseudohypo leaves following manufacturer directions.

We collected four $A \textendash g_\text{sw}$ curves per leaf, an amphi (untreated) curve and a pseudohypo (treated) curve at high light-intensity ($\mathrm{PPFD} = \qty{2000}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$) and low light-intensity ($\mathrm{PPFD} = \qty{150}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$). We always measured high light-intensity curves first because photosynthetic downregulation is faster than upregulation in these species. To control for order effects, we alternated between starting with amphi or pseudohypo leaf measurements. Unlike @triplett_amphistomy_2024, preliminary experiments with *Solanum* indicated a strong order effect in that $A$ declined in the second curve. Therefore, we made measurements over two days. On the first day, we measured high and low light-intensity curves for either amphi or pseudohypo leaves; on the second day, we measured high and low light-intensity curves on the other leaf type.

In all cases, we acclimated the focal leaf to high light ($\mathrm{PPFD} = \qty{2000}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$) and high relative humidity ($\mathrm{RH} = 70\%$) until $A$ and $g_\text{sw}$ reach their maximum. After that, we decreased $\mathrm{RH}$ to $\approx 10\%$ to induce rapid stomatal closure without biochemical downregulation. Hence, $A_\text{amphi}$ and $A_\text{hypo}$ were both measured at low chamber humidity after the leaf had acclimated to high humidity. All other environmental conditions in the leaf chamber remained the same. We logged data until $g_\text{sw}$ reached its nadir. We then acclimated the leaf to low light ($\mathrm{PPFD} = \qty{150}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$) and 70\% $\mathrm{RH}$ before inducing stomatal closure with low $\mathrm{RH}$.

>>>>

---
title: Unknown
format:
  pdf:
    keep-tex: true  
    toc: false
header-includes: |
  \addtokomafont{disposition}{\rmfamily}
  \usepackage{siunitx}
  \newcommand{\agcurve}{$A \textendash g_\text{sc}$}
  \newcommand{\gsc}{$g_\text{sc}$}
  \newcommand{\ppfd}{$\mathrm{PPFD}$}
  \newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
  \newcommand{\rh}{$\mathrm{RH}$}
mainfont: Times New Roman
csl: https://www.zotero.org/styles/science
---

@@

#### Amphistomy advantage

We estimated 'amphistomy advantage' ($\mathrm{AA}$) *sensu* @parkhurst_adaptive_1978, but with modifications previously described in @triplett_amphistomy_2024. $\mathrm{AA}$ is calculated as the log-response ratio of $A$ compared at the same total \gsc:

@@

We measured the photosynthetic rate of an untreated amphistomatous leaf ($A_{\mathrm{amphi}}$) over a range of \gsc values. We refer to this as an \agcurve curve. We compared the \agcurve curve of the untreated leaf to the photosynthetic rate of pseudohypostomatous leaf ($A_\mathrm{hypo}$), which is the same leaf but with gas exchange through the upper surface blocked by a neutral density plastic (propafilm).

We measured \agcurve curves using a portable infrared gas analyzer (LI-6800PF, LI-COR Biosciences, Lincoln, Nebraska, USA). Light-acclimated plants were placed under LEDs dimmed to match their light treatment during gas exchange measurements. We estimated the photosynthetic rate ($A$) and stomatal conductance to CO$_2$ (\gsc) at ambient CO$_2$ (415 ppm) and $T_\mathrm{leaf} = \qty{25.0}{\degreeCelsius}$. The irradiance of the light source in the pseudohypo leaf was higher because the propafilm reduces transmission. To compensate for reduced transmission, we increased incident \ppfd for pseudohypo leaves by a factor 1/0.91, the inverse of the measured transmissivity of the propafilm. We also set the stomatal conductance ratio, for purposes of calculating boundary layer conductance, to 0 for pseudohypo leaves following manufacturer directions.

We collected four \agcurve curves per leaf, an amphi (untreated) curve and a pseudohypo (treated) curve at high light-intensity (\ppfdequals{2000}) and low light-intensity (\ppfdequals{150}). We always measured high light-intensity curves first because photosynthetic downregulation is faster than upregulation in these species. To control for order effects, we alternated between starting with amphi or pseudohypo leaf measurements. Unlike @triplett_amphistomy_2024, preliminary experiments with *Solanum* indicated a strong order effect in that $A$ declined in the second curve. Therefore, we made measurements over two days. On the first day, we measured high and low light-intensity curves for either amphi or pseudohypo leaves; on the second day, we measured high and low light-intensity curves on the other leaf type.

In all cases, we acclimated the focal leaf to high light (\ppfdequals{2000}) and high relative humidity ($\mathrm{RH} = 70\%$) until $A$ and \gsc reach their maximum. After that, we decreased \rh to $\approx 10\%$ to induce rapid stomatal closure without biochemical downregulation. Hence, $A_\text{amphi}$ and $A_\text{hypo}$ were both measured at low chamber humidity after the leaf had acclimated to high humidity. All other environmental conditions in the leaf chamber remained the same. We logged data until \gsc reached its nadir. We then acclimated the leaf to low light (\ppfdequals{150}) and 70\% \rh before inducing stomatal closure with low \rh and logging data as described above.

#### Light-response curves

We measured light-response curves on the same leaflets as \agcurve curves

testing \gsc

### 2024-03-06 ms/ms.tex
started adding latex shortcuts to ms

\KOMAoption{captions}{tableheading}
\addtokomafont{disposition}{\rmfamily}
\usepackage{siunitx}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Unknown},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, interior hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

We compared AA among 30 ecologically diverse accessions of wild tomato,
including representatives of all described species of \emph{Solanum}
sect. \emph{Lycopersicon} and sect. \emph{Lycopersicoides}
{[}@peralta\_taxonomy\_2008{]} and the cultivated tomato \emph{S.
lycopersicum} var. \emph{lycopersicum} (tab:accessions). Seeds provided
by the Tomato Genetics Resource Center germinated on moist paper in
plastic boxes after soaking for 30-60 minutes in a 50\% (volume per
volume) solution of household bleach and water, followed by a thorough
rinse. We transferred seedlings to cell-pack flats containing Pro-Mix BX
potting mix (Premier Tech, Rivière-du-Loup, Quebec, Canada) once
cotyledons fully emerged, typically within 1-2 weeks of sowing. We grew
seeds and seedlings for both sun and shade treatments under the same
environmental conditions (12:12 h, 25:\(\qty{20}{\degreeCelsius}\),
40:60 RH day:night cycle). LED light provided
\(\mathrm{PPFD} = \qty{200}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}\).

After seedlings established in cell-pack flats for \(\approx 2\) weeks,
we transplanted them to 3.78 L plastic pots containing 60\% Pro-Mix BX
potting mix, 20\% coral sand (Pro-Pak, Honolulu, Hawaiʻi, USA), and 20\%
cinders (Niu Nursery, Honolulu, Hawaiʻi, USA). Percentage composition is
on a volume basis. The soil mixture contained slow release NPK
fertilizer following manufacturer instructions (Osmocote Smart-Release
Plant Food Flower \& Vegetable, The Scotts Company, Marysville, Ohio,
USA).

outline of tab:accessions LA number,Species name, lat, lon, elev, SPLASH
light value

>>>>

\KOMAoption{captions}{tableheading}
\addtokomafont{disposition}{\rmfamily}
\usepackage{siunitx}
\newcommand{\gsc}{$\g_text{sc}$}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Unknown},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

We compared AA among 30 ecologically diverse accessions of wild tomato,
including representatives of all described species of \emph{Solanum}
sect. \emph{Lycopersicon} and sect. \emph{Lycopersicoides}
{[}@peralta\_taxonomy\_2008{]} and the cultivated tomato \emph{S.
lycopersicum} var. \emph{lycopersicum} (tab:accessions). Due to
constraints on growth space and time, we spread out measurements over 80
weeks from May 1, 2022 to October 31, 2023. Replicates within accession
were evenly spread out over this period to prevent confounding of
temporal variation in growth conditions with accession. {[}anything else
to say here? maybe explain accession selection and phylogeny?{]}

\begin{table}

\end{table}

\hypertarget{plant-growth-conditions}{%
\subsubsection{Plant growth conditions}\label{plant-growth-conditions}}

In all growth spaces, we recorded \(\mathrm{PPFD}\) using full spectrum
quantum sensors (SQ-500-SS, Apogee Instruments, Logan, Utah, USA); we
recorded temperature, RH, and {[}CO\(_2\){]} using an EE894 sensor (E+E
Elektronik, Engerwitzdorf, Austria) protected by a radiation shield. All
environmental measurements were taken every 10 minutes from the middle
of plants racks at approximately the same height as the leaves we
measured. We measured leaf temperature of focal leaves prior to
measurement using an infrared radiometer (SI-111-SS, Apogee Instruments,
Logan, Utah, USA).

\hypertarget{germination-and-seedling-stage}{%
\paragraph{Germination and seedling
stage}\label{germination-and-seedling-stage}}

Seeds provided by the Tomato Genetics Resource Center germinated on
moist paper in plastic boxes after soaking for 30-60 minutes in a 50\%
(volume per volume) solution of household bleach and water, followed by
a thorough rinse. We transferred seedlings to cell-pack flats containing
Pro-Mix BX potting mix (Premier Tech, Rivière-du-Loup, Quebec, Canada)
once cotyledons fully emerged, typically within 1-2 weeks of sowing. We
grew seeds and seedlings for both sun and shade treatments under the
same environmental conditions (12:12 h, 25:\(\qty{20}{\degreeCelsius}\),
40:60 RH day:night cycle). LED light provided
\(\mathrm{PPFD} = \qty{200}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}\)
(Fluence RAZRx, Austin, Texas, USA).

\hypertarget{light-treatments}{%
\paragraph{Light treatments}\label{light-treatments}}

Seedlings were randomly assigned in alternating order within accession
to the sun or shade treatment during transplanting. After seedlings
established in cell-pack flats for \(\approx 2\) weeks, we transplanted
them to 3.78 L plastic pots containing 60\% Pro-Mix BX potting mix, 20\%
coral sand (Pro-Pak, Honolulu, Hawaiʻi, USA), and 20\% cinders (Niu
Nursery, Honolulu, Hawaiʻi, USA). Percentage composition is on a volume
basis. The soil mixture contained slow release NPK fertilizer following
manufacturer instructions (Osmocote Smart-Release Plant Food Flower \&
Vegetable, The Scotts Company, Marysville, Ohio, USA). We determined pot
field capacity one week after transplanting using a scale (Ohaus V12P15
Valor 1000, Parsippany, New Jersey, USA) and watered to field capacity
three times per week to prevent drought stress.

We assigned sun and shade treatment to lower and upper racks of a
\(\qty{1.22}{\meter} \times \qty{2.44}{\meter}\) shelving unit in a
climate-controlled growth room. We assigned the sun treatment to the
lower rack to limit diffuse light from reaching the shade treatment. The
average daytime \(\mathrm{PPFD}\) was
\(\qty{800}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}\) and
\(\qty{125}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}\) for sun
and shade treatments, respectively. To isolate the effect of light
intensity from quality, we used the same LED model with the the same
spectrum (Fluence SPYDR 2i, Austin, Texas, USAS), but dimmed the lights
in the shade treatment. To maintain homogeneous environmental conditions
other than light, we mixed air within the growth room using an air
circulator (Vornado 693DC, Andover, Kansas, USA) and within racks using
a miniature oscillating air circulator (Vornado Atom 1, Andover, Kansas,
USA). Despite these efforts, the air in the sun treatment was on average
\(\qty{1}{\degreeCelsius}\) warmer and the average RH was consequently 5
lower. However, because of evaporative cooling, the leaves in the sun
treatment were only \(\qty{1}{\degreeCelsius}\) on average (\(n = 600\)
leaves).

\hypertarget{leaf-trait-measurements}{%
\subsubsection{Leaf trait measurements}\label{leaf-trait-measurements}}

We selected a fully expanded, unshaded leaf at least six leaves above
the cotyledons during early vegetative growth. This typically meant that
plants had grown in light treatments for \(\approx\) 4 weeks, ensuring
they had time to sense and respond developmentally to the light
intensity of the treatment rather than the seedling conditions
{[}@schoch\_dependence\_1980{]}. Shade plants grew slower than sun
plants, hence leaves at the same developmental stage were measured on
chronologically older plants in the shade treatment. In some sun plants,
we had to use leaves higher on the stem because short internodes made
lower leaves inaccessible with the gas exchange equipment. We measured
terminal leaflets in 70.0\% of cases, but used the lateral leaflet
closest to the terminal leaflet when it was damaged or difficult to
clamp into the gas exchange chamber. When a leaflet was damanged during
gas exchange measurements, we collected anatomical data from the nearest
leaflet on the same leaf (10.0)\%. We measured chlorophyll concentration
index (CCI) using a chrolophyll concentration meter (MC-100, Apogee
Instruments, Logan, Utah, USA) on the lamina of focal leaflets before
gas exchange measurements at the same time we measured leaf temperature.

\hypertarget{amphistomy-advantage}{%
\paragraph{Amphistomy advantage}\label{amphistomy-advantage}}

We estimated `amphistomy advantage' (\(\mathrm{AA}\)) \emph{sensu}
@parkhurst\_adaptive\_1978, but with modifications previously described
in @triplett\_amphistomy\_2024. \(\mathrm{AA}\) is calculated as the
log-response ratio of \(A\) compared at the same total \(g_\text{sw}\):

\[\mathrm{AA} = \mathrm{log}(A_{\mathrm{amphi}} / A_{\mathrm{hypo}})\]

We measured the photosynthetic rate of an untreated amphistomatous leaf
(\(A_{\mathrm{amphi}}\)) over a range of \(g_\text{sw}\) values. We
refer to this as an \(A \textendash g_\text{sw}\) curve. We compared the
\(A \textendash g_\text{sw}\) curve of the untreated leaf to the
photosynthetic rate of pseudohypostomatous leaf (\(A_\mathrm{hypo}\)),
which is the same leaf but with gas exchange through the upper surface
blocked by a neutral density plastic (propafilm).

We measured \(A \textendash g_\text{sw}\) curves using a portable
infrared gas analyzer (LI-6800PF, LI-COR Biosciences, Lincoln, Nebraska,
USA). Light-acclimated plants were placed under LEDs dimmed to match
their light treatment during gas exchange measurements. We estimated the
photosynthetic rate (\(A\)) and stomatal conductance to water vapor
(\(g_\text{sw}\)) at ambient CO\(_2\) (415 ppm) and
\(T_\mathrm{leaf} = \qty{25.0}{\degreeCelsius}\). The irradiance of the
light source in the pseudohypo leaf was higher because the propafilm
reduces transmission. To compensate for reduced transmission, we
increased incident \(\mathrm{PPFD}\) for pseudohypo leaves by a factor
1/0.91, the inverse of the measured transmissivity of the propafilm. We
also set the stomatal conductance ratio, for purposes of calculating
boundary layer conductance, to 0 for pseudohypo leaves following
manufacturer directions.

We collected four \(A \textendash g_\text{sc}\) curves per leaf, an
amphi (untreated) curve and a pseudohypo (treated) curve at high
light-intensity
(\(\mathrm{PPFD} = \qty{2000}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}\))
and low light-intensity
(\(\mathrm{PPFD} = \qty{150}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}\)).
We always measured high light-intensity curves first because
photosynthetic downregulation is faster than upregulation in these
species. To control for order effects, we alternated between starting
with amphi or pseudohypo leaf measurements. Unlike
@triplett\_amphistomy\_2024, preliminary experiments with \emph{Solanum}
indicated a strong order effect in that \(A\) declined in the second
curve. Therefore, we made measurements over two days. On the first day,
we measured high and low light-intensity curves for either amphi or
pseudohypo leaves; on the second day, we measured high and low
light-intensity curves on the other leaf type.

In all cases, we acclimated the focal leaf to high light
(\(\mathrm{PPFD} = \qty{2000}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}\))
and high relative humidity (\(\mathrm{RH} = 70\%\)) until \(A\) and
\(g_\text{sw}\) reach their maximum. After that, we decreased
\(\mathrm{RH}\) to \(\approx 10\%\) to induce rapid stomatal closure
without biochemical downregulation. Hence, \(A_\text{amphi}\) and
\(A_\text{hypo}\) were both measured at low chamber humidity after the
leaf had acclimated to high humidity. All other environmental conditions
in the leaf chamber remained the same. We logged data until
\(g_\text{sc}\) reached its nadir. We then acclimated the leaf to low
light
(\(\mathrm{PPFD} = \qty{150}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}\))
and 70\% \(\mathrm{RH}\) before inducing stomatal closure with low
\(\mathrm{RH}\) and logging data as described above.

\hypertarget{light-response-curves}{%
\paragraph{Light-response curves}\label{light-response-curves}}

We measured light-response curves on the same leaflets as
\(A \textendash g_\text{sc}\)

testing \gsc

### 2024-03-06 ms/test.qmd
started adding latex shortcuts to ms

---
title: Unknown
format:
  pdf:
    keep-tex: true  
    toc: false
header-includes: |
  \addtokomafont{disposition}{\rmfamily}
  \usepackage{siunitx}
mainfont: Times New Roman
csl: https://www.zotero.org/styles/american-journal-of-botany
---

words $\qty{4}{\micro\meter}$

(12:12 $\qty{25}{\degreeCelsius}$

and then this $\qty{200}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$

$\qty{0.1}{\hertz}$

>>>>

---
title: Unknown
format:
  pdf:
    keep-tex: true  
    toc: false
header-includes: |
  \addtokomafont{disposition}{\rmfamily}
  \usepackage{siunitx}
  \newcommand{\gsc}{$g_\text{sc}$}
  \newcommand{\ppfd}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
mainfont: Times New Roman
csl: https://www.zotero.org/styles/american-journal-of-botany
---

words \gsc

this \ppfd{2000}
